Share Buyback and Equity Issue Anomalies Revisited

### 2016-03-03 bb_issuers.Rnw
update

%%Blind title page
%\begin{titlepage}
%\begin{center}
%  \centering
%\vskip 60pt
%\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
%\vskip 1.5em
%\normalsize  \today
%\noindent \\ 
%\begin{abstract}
%\noindent We re-examine the behavior of stock returns after net issue  announcements using the five-factor model proposed by Fama and French (2015a). We confirm their findings that the equity issue anomaly disappears  with the five-factor model, but the buyback anomaly does not.. Buyback announcements by firms  with high pre-announcement (idiosyncratic) volatility  are followed by higher long-term abnormal returns. This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
%\end{abstract}
%\vspace{2cm}
%\end{center}
%\medskip
%\noindent \textit{JEL classification}: G35
%\medskip
%\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings
%\end{titlepage}

@@

The fact that companies experience long-term positive excess returns after share buybacks and negative long term excess returns after equity issues, has been documented extensively in the academic literature.\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}. For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}  In spite of these well documented anomalies investors are not less excited today about e.g., a buyback announcement than 30 years ago: on average stock prices increase by approximately 2 to 3$\%$ when companies announce that the board of directors has approved a buyback program. Moreover, we find very few funds that specialize in exploiting these anomalies.\footnote{  For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA. The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization. We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} The fact that these anomalies have not generated a significant response from investors and asset management firms is somewhat surprising considering that other anomalies have disappeared after being documented in academic research~\citep{McLean2015}. What makes these capital structure anomalies different so that they stand the test of time?

One straightforward explanation is that they are not really anomalous returns but compensation for risk. Excess returns in previous research are calculated using the \cite{FamaFrench1993} three-factor model or the Carhart (1997) 4-factor model as benchmarks. However, \cite{FamaFrench2015b} argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns. This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns (Novy-Marx (2013)). If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research. Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies. First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}. For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization (Stephens and Weisbach (1998)). Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues). The part of their sample where net equity issues are positive is defined as the ``buyback sample''. But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations. Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares. However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors. In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only takes advantage of selling shareholders who leave the firm. In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.

A second possible reason for the funds' lack of interest in the buyback anomaly is that event studies aggregate returns over a very long horizon. The fact that buying shares after a buyback announcement generates positive excess returns during for example 1990-2014 does not mean that, if one starts a fund in 2016, one can expect to beat the market during the next 3 years. In other words, the anomaly may be time dependent, and investor patience may not extend beyond 3 years. Moreover, because of the growth of institutional investors and the reduction in trading costs markets may have become more efficient in recent years as argued by \cite{FuHuang2015}. The anomaly may also be industry-specific so that an investor who follows a buyback strategy may end up with a highly undiversified portfolio.

The long-term event studies also do not give much guidance about when to sell after a buyback or cover after shorting an equity issue. Trading strategies, such as $M\&A$ arbitrage (\cite{MitchellPulvino2001}), often have ``natural'' exit decision points (e.g., at $M\&A$ deal completion or termination), but the literature does not provide clear guidance about when to exit a buyback position.  Empirical studies tend to show that, on average, excess returns continue for up to 3 or 4 years after a buyback authorization, but there is no reason why such a horizon is optimal. One straightforward ``early'' selling strategy that we study is to combine the buyback and equity issuance anomalies by selling buyback stocks after the firm announces an equity issue. Note that the fact that equity issues in general are followed by negative abnormal returns does not necessarily imply that equity issues after buybacks should generate the same result.

Finally, the results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously. Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information. If the buyback signals a change in risk (\cite{GrullonMichaely2004}) hedging market risk may be complicated. That is why in this paper we also simulate hedged investment strategies where we estimate risk {\it before} forming the portfolios.

The purpose of this paper is to explore these concerns by studying the robustness of the buybacks and issuance anomalies over the 30 year period starting in January \Sexpr{firstyear} and ending in December \Sexpr{lastyear}, using the \cite{FamaFrench2015a} five-factor model. Although there are other models of market equilibrium proposed to explain excess returns after buyback authorizations (i.e. \cite{Linetal2014}) our focus is on the \cite{FamaFrench2015a} challenge.  We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. The interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive. We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries.

We also test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}: that (idiosyncratic) volatility is negatively related to future returns. For example, \cite{Ang2006} find negative alphas for high volatility and high idiosyncratic volatility stocks, using the 3 factor \cite{FamaFrench1993} model. Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms. However, in our buyback sample we find a significant positive relation between excess returns, using  the Fama-French 5-factor model as a benchmark. This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market. The result is also consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  stocks.

Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns. This is consistent with the {\it option hypothesis}:  a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks (\cite{IkenberryVermaelen1996}). If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.  Combining idiosyncratic risk and total volatility  with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

@@

We report the returns of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns. Specifically, at the end of \Sexpr{lastyear} the cumulative returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$. This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer. However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period. Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.  The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}. In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.

@@

There exists a large literature on volatility and stock returns. One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3 factor \cite{FamaFrench1993} model  (see e.g. \cite{Ang2006} (Table VII)). This volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.  Perhaps the buyback and the volatility anomaly are related: are the buyback firms with the largest excess returns also firms with the smallest (idiosyncratic) risk?  Or can we make arguments that the opposite is true, if we accept the fundamental proposition of this paper, i.e. that excess returns are a result of the fact that managers are on average successful in taking advantage of an undervalued stock price?

@@

The main ``theory'' behind the buyback anomaly is that firms may have superior {\it company-specific} information. Such situations are more likely in industries or companies where the value is driven less by market wide factors, i.e., by highly ``idiosyncratic'' companies.  So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between idiosyncratic returns and volatility.  To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month, or using the idiosyncratic volatility as in \cite{Ang2006}, leads to the same conclusions - results available upon request. However, as we want to differentiate between ``idiosyncratic'' companies and ``high volatility'' ones, to consider both the effects of company specific information and of the option value of a buyback announcement, we separately study the relations with $R^2$ and volatility. See also \cite{Lietal2014} for a discussion on this issue.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$. We also define the idiosyncratic score of a firm to be the percentile of its $1-R^2$ across all CRSP firms that month. Note that we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only. Table~\ref{tbl:industriesR2Vol}, columns (1) and (2) show the percentage of high and low idiosyncratic risk events across all industries for which we have at least 100 buyback events in our sample. The healthcare industry has the largest percentage of firms classified as ``high idiosyncratic'', while cyclical industries such as steel, construction and chemicals contain a large number of ``low idiosyncratic'' firms.

@@

The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \cite{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns. However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks. Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing. Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.  Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).

@@

The announcement of a buyback program is not a firm commitment, but an option to buy back stock. Ikenberry and Vermaelen (1996) model this flexibility as an exchange option in which the market price of the stock is exchanged for the true value of the stock. They predict that, as with all options, the value increases with the volatility. The intuition is that the larger the volatility, the larger the probability that the market price may deviate from the true value. This enhances the timing ability of the manager-insider.  They show that this option can have a lot of value, something that may not be realized at the time of the announcement of the buyback authorization.  Hence, perhaps total volatility is a better prediction of excess returns than idiosyncratic volatility or the U-index.  Or perhaps volatility can be an additional, next to the U-index and idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.

>>>>

%%Blind title page
%\begin{titlepage}
%\begin{center}
%  \centering
%\vskip 60pt
%\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
%\vskip 1.5em
%\normalsize  \today
%\noindent \\ 
%\begin{abstract}
%\noindent We re-examine the behavior of stock returns after net issue  announcements using the five-factor model proposed by Fama and French (2015a). We confirm their findings that the equity issue anomaly disappears  with the five-factor model, but the buyback anomaly does not. Buyback announcements by firms  with high pre-announcement (idiosyncratic) volatility  are followed by higher long-term abnormal returns. This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
%\end{abstract}
%\vspace{2cm}
%\end{center}
%\medskip
%\noindent \textit{JEL classification}: G35
%\medskip
%\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings
%\end{titlepage}

@@

The fact that companies experience long-term positive excess returns after share buybacks and negative long term excess returns after equity issues, has been documented extensively in the academic literature.\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}. For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}  In spite of these well documented anomalies investors are not less excited today about e.g., a buyback announcement than 30 years ago: on average stock prices increase by approximately 2 to 3$\%$  when companies announce that the board of directors has approved a buyback program. Moreover, we find very few funds that specialize in exploiting these anomalies.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA. The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization. We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} The fact that these anomalies have not generated a significant response from investors and asset management firms is somewhat surprising considering that other anomalies have disappeared after being documented in academic research~\citep{McLean2016}. What makes these capital structure anomalies different so that they stand the test of time?

One straightforward explanation is that they are not really anomalous returns but compensation for risk. Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the Carhart (1997) 4-factor model as benchmarks. However, \cite{FamaFrench2015b}  argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns. This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns (Novy-Marx (2013)). If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research. Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies. First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}. For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization (Stephens and Weisbach (1998)). Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues). The part of their sample where net equity issues are positive is defined as the "buyback sample". But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations. Moreover the idea of pooling buybacks and equity issues in "net issues" assumes that the decision to issue equity is simply the mirror of buying back shares. However, issuing stock to new investors is not the same as buying back stock from "old" selling investors. In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only takes advantage of selling shareholders who leave the firm. In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.

Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the Fama and French (2015b) conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. The interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive. We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries. The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.

The results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously. Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information. If the buyback signals a change in risk (\cite{GrullonMichaely2004}) hedging market risk may be complicated. That is why in this paper we also simulate hedged investment strategies where we estimate risk before forming the portfolios. We show that an investor who followed this strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.

The second major purpose of this paper is to test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}, i.e. (idiosyncratic) volatility is negatively related to expected returns. For example, \cite{Ang2006} find negative alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model. Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms. However, in our buyback sample we find a significant positive relation between excess returns, using the Fama-French 5-factor model as a benchmark. This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market. The result is also consistent with the  {\it costly arbitrage hypothesis} of \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued  stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  Their argument is that idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing.  So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.

Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns. This is consistent with the {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks (\cite{IkenberryVermaelen1996}). If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.

Combining idiosyncratic risk and total volatility with the Peyer and Vermaelen (2009) Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

@@

We report the returns and excess returns of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns. Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$. This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer. However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period. Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.  The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}. In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.

@@

There exists a large literature on volatility and stock returns.\footnote{For the most recent overview of the literature and potential hypotheses, see \cite{LiRodneyGarcia2016}.} One of the most puzzling findings is the fact that total volatility and idiosyncratic volatility are negatively correlated with future abnormal returns, when expected returns are calculated using the 3 factor \cite{FamaFrench1993} model  (see e.g. \cite{Ang2006} (Table VII)). This volatility anomaly also survives after using the \cite{FamaFrench2015a} 5-factor model, at least for small firms.  Perhaps the buyback and the volatility anomaly are related: are the buyback firms with the largest excess returns also firms with the smallest (idiosyncratic) risk?  Or can we make arguments that the opposite is true, if we accept the fundamental proposition of this paper, i.e. that excess returns are a result of the fact that managers are on average successful in taking advantage of an undervalued stock price?

@@

The main ``theory'' behind the buyback anomaly is that firms may have superior {\it company-specific} information. Such situations are more likely in industries or companies where the value is driven less by market wide factors, i.e., by highly ``idiosyncratic'' companies.  So if buybacks are driven by market timing this superior information hypothesis predicts that there should be a positive relation between idiosyncratic returns and volatility.  To test this hypothesis, for each event we measure the five-factor regression $R^2$ using the 6-months daily returns just before the event announcement.\footnote{Using shorter time windows, e.g., 1 month, or using the idiosyncratic volatility as in \cite{Ang2006}, leads to the same conclusions - results available upon request. However, as we want to differentiate between ``idiosyncratic'' companies and ``high volatility'' ones, to consider both the effects of company specific information and of the option value of a buyback announcement, we separately study the relations with $R^2$ and volatility. See also \cite{LiRajgopaletal2014} for a discussion on this issue.} We define two types of events: ``low idiosyncratic'' (high $R^2$) and ``high idiosyncratic'' (low $R^2$) events, depending on whether the five-factor regression $R^2$ was in the top or bottom \Sexpr{round(100*quantile_R2,2)}$\%$ of the $R^2$ of all CRSP companies: each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' five-factor regression $R^2$. We also define the idiosyncratic score of a firm to be the percentile of its $1-R^2$ across all CRSP firms that month. Note that we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only. Table~\ref{tbl:industriesR2Vol}, columns (1) and (2) show the percentage of high and low idiosyncratic risk events across all industries for which we have at least 100 buyback events in our sample. The healthcare industry has the largest percentage of firms classified as ``high idiosyncratic'', while cyclical industries such as steel, construction and chemicals contain a large number of ``low idiosyncratic'' firms.

@@

The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \cite{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns. However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks. Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing. Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.  Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).  So our results are also consistent with the \cite{Stambaugh2015} interpretation.

@@

The announcement of a buyback program is not a firm commitment, but an option to buy back stock. Ikenberry and Vermaelen (1996) model this flexibility as an exchange option in which the market price of the stock is exchanged for the true value of the stock. They predict that, as with all options, the value increases with the volatility. The intuition is that the larger the volatility, the larger the probability that the market price may deviate from the true value. This enhances the timing ability of the manager-insider.  They show that this option can have a lot of value, something that may not be realized at the time of the announcement of the buyback authorization.  For example, the market may underestimate the maturity of the option if they don't realize that firms who are announcing a buyback authorization for say 2 years are likely to renew the authorization many times in the future.   Hence, perhaps total volatility is a better prediction of excess returns than idiosyncratic volatility or the U-index.  Or perhaps volatility can be an additional, next to the U-index and idiosyncratic volatility, indicator of the likelihood that the buyback is driven by undervaluation.
